Calculating Entropies With Nested Sampling

### 2017-01-22 paper/ms.tex
Wrote a bit about the gaussian problem
results
Differential entropy of p(d) for normal example

>>>>

Consider the basic problem of inferring a quantity $\mu$ from
100 observations $\x = \{x_1, ..., x_{100}\}$ whose probability distribution
(conditional on $\mu$) is
\begin{align}
p(x_i | \mu) &\sim \textnormal{Normal}(\mu, 1).
\end{align}
If the prior for $\mu$ is Normal$(0, 10^2)$, then the posterior is
\begin{align}
\mu | \x &\sim \textnormal{Normal}\left(
                                       \frac{1}{100}\sum_{i=1}^{100} x_i,
                                       \left[\frac{10}{\sqrt{10001}}\right]^2
                                       \right).
\end{align}

\begin{align}
H_{\d} &=% 945.42 \pm 1.02 \\ % 1000 mcmc steps
         % 929.26 \pm 1.00 \\ % 2000 mcmc steps
         % 927.40 \pm 0.98 \\ % 3000 mcmc steps
         % 927.26 \pm 1.00 \\ % 4000 mcmc steps
          928.21 \pm 1.00    % 5000 mcmc steps
\end{align}
The log-volume of a 100-dimensional ball of radius $10^{-3}$ is
-782.017. Therefore, the measured differential entropy of
$p(\d)$ is $928.21 - 782.017 = 146.19 \pm 1.00$, consistent with the
true value of $146.499$.
